Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-10-01 methods_paper/fabl-paper.tex
update.
BK edits on 4.3, Fast Beta Prior

\[\lambda \sim \text{Beta}(\alpha_{\lambda}, \beta_{\lambda}) \] The
prior for \(Z_j\) has equal probability of matching to all records
\(i\in A\), and non-matching probability governed by \(\lambda\).
Therefore a \(\lambda \sim \text{Beta}(1, 1)\) corresponds to a prior
belief that nonmatches and matches are equally likely, and a
\(\lambda \sim \text{Beta}\left(1, \frac{1}{n_1}\right)\) prior
corresponds to a uniform prior on the labeling of \(\mathbf{Z}\).

\begin{remark}
There is a clear relationship between our proposed model and that of \cite{sadinle_bayesian_2017}. 
\cite{sadinle_bayesian_2017} constructs a prior distribution on the entire \(\mathbf{Z}\) vector, 
which induces a Gibbs
sampler that strictly enforces one-to-one matching. In particular, this
sampler removes previously matches records from the set of candidate
records when sampling \(Z_j\), creating a dependency that makes the
sampler \emph{inherently serial}. On the other hand, we propose 
 independent priors for
each \(Z_j\), creating a sampler that is \emph{embarassingly parallel}, allowing for significant computational gains. 
More importantly, since only the agreement pattern of \(Z_j\) is used for
calculations within the Gibbs sampler, and not the particular record
label, this sampling is only needed at the level of the unique agreement patterns, which offers additional computational savings.  In doing so however, we thereby weaken the one-to-one requirement from
\texttt{BRL}; our sampler does ensure that each record in \(\bm{X}_2\) can be
matched to at most one record in \(\bm{X}_1\), but allows for the possibility
that multiple records in \(\bm{X}_2\) match to the same record in \(\bm{X}_1\). We resolve contradictions via a post-processing step \textcolor{red}{state what the post-processing step is Brian}. 
\end{remark}

@@

\newpage
\textcolor{red}{RCS: I stopped here.}
\hypertarget{posterior-sampling}{%
	\subsection{Gibbs Sampler}
	\label{gibbs_sampling}}
We work with the following factorization of the joint posterior distribution:

@@

>>>>

\[\lambda \sim \text{Beta}(\alpha_{\lambda}, \beta_{\lambda}) \]

{
	\color{blue}
	Intuitively, this set of priors says that record $j \in \bm{X}_2$ has some match in $\bm{X}_1$ with probability $\lambda$, and that each record $i \in \bm{X}_1$ is equally likely to be that match. $\lambda$ itself is given a prior distribution to reflect prior beliefs about the overall rate of matchingness in the data. One choice of uninformative prior might be \(\lambda \sim \text{Beta}(1, 1)\), which corresponds to a prior belief that nonmatches and matches are equally likely, and another might be \(\lambda \sim \text{Beta}\left(1, \frac{1}{n_1}\right)\), which corresponds to a uniform prior on the labeling of \(\mathbf{Z}\).
}

%The prior for \(Z_j\) has equal probability of matching to all records
%\(i\in A\), and non-matching probability governed by \(\lambda\).

{
\color{blue}
There is a clear relationship between our proposed model and that of \cite{sadinle_bayesian_2017}. 
\cite{sadinle_bayesian_2017} constructs a prior distribution on the entire \(\mathbf{Z}\) vector, called the \emph{beta distribution for bipartite matching}, given by
$$P(\mathbf{Z}|\alpha_{\pi}, \beta_{\pi}) = \frac{(n_1 - n_{12}(\mathbf{Z}))!}{n_1 !}\frac{\text{B}(n_{12}(\mathbf{Z}) + \alpha_{\pi}, n_2 - \mathbf{Z}) - \beta_{\pi}])}{\text{B}(\alpha_{\pi}, \beta_{\pi})}
$$
where $\text{B}(\cdot, \cdot)$ represents the Beta function. This prior induces a Gibbs sampler that strictly enforces one-to-one matching,  previously matched records from the set of candidate
records when sampling \(Z_j\). This creates a dependency that makes the
sampler \emph{inherently serial}.

On the other hand, we propose independent priors for each \(Z_j\), creating a sampler that is \emph{embarassingly parallel}, allowing for significant computational gains. More importantly, since only the agreement pattern of \(Z_j\) is used for
calculations within the Gibbs sampler, and not the particular record
label, this sampling is only needed at the level of the unique agreement patterns, which offers additional computational savings.  In doing so however, we thereby weaken the one-to-one requirement from
\texttt{BRL}; our sampler does ensure that each record in \(\bm{X}_2\) can be
matched to at most one record in \(\bm{X}_1\), but allows for the possibility
that multiple records in \(\bm{X}_2\) match to the same record in \(\bm{X}_1\). \textcolor{blue}{We resolve contradictions when calcuating the Bayes estimate, which is explained in Section 4.5}

NOTE TO BEKA: I think it will be best to do the "post-processing step" along with the Bayes Estimate. Its equivalent to minimizing the posterior loss subject to the constraint that $Z_j \neq Z_{j'}, \forall j \neq j'$.
}

@@

\hypertarget{posterior-sampling}{%
	\subsection{Gibbs Sampler}
	\label{gibbs_sampling}}
We work with the following factorization of the joint posterior distribution:

@@

\textcolor{red}{RCS: I stopped here.}
